Using demographic accounts to enhance official population statistics

### 2021-11-06 article.tex
Updates from Overleaf

A slightly more complicated example is
\begin{center}
\includegraphics[width=0.5\textwidth]{figures_accounts/fig_account_region.pdf}
\end{center}
Rather than treating the population as a completely homogenous, this account recognizes two subpopulations, labelled ``A'' and ``B''. A and B might, for instance, denote geographical region, health status, or labour force status. In this example, for simplicity, we allow for movement between the two statuses, but no births, deaths, or other forms of entry or exit to the system as a whole. The demographic accounting identities can be applied separately to each group,
\begin{align*}
    11 - 15 & = -5 + 1 \quad \text{(A)}\\
    14 - 10 & = -1 + 5 \quad \text{(B)}.
\end{align*}
When the accounting identities for each group are satisfied, the accounting identity for the system is a whole is necessarily satisfied as well.

@@

Publishers of age-structured demographic data typically use some variant of the following scheme,
\begin{center}
\includegraphics[width=0.5\textwidth]{figures_accounts/fig_account_withage2.pdf}
\end{center}
Population stocks stocks and flows are all disaggregated by the same age groups, which, in the case above, are ages 0, 1, and 2+. (The account in question might apply to non-human animals, or use a unit of measurement that is longer than a year.) The final age group includes everone over a certain age. Births are disaggregated by the age of the mother, rather than the age of the child being born, which is always 0.

@@

\begin{align}
    6 - (5 + 4) & = -0 + -1 + -2 \quad \text{(Age 2+ at $t+1$)} \\
    5 - 7 & = -1 + -1 \quad \text{(Age 1 at $t+1$)} \\
    6 - (3 + 5) & = -2    
\end{align}

>>>>

A slightly more complicated example is
\begin{center}
\includegraphics[width=0.7\textwidth]{figures_accounts/fig_account_region.pdf}
\end{center}
Rather than treating the population as a completely homogenous, this account recognizes two subpopulations, labelled ``A'' and ``B''. A and B might, for instance, denote geographical region, health status, or labour force status. In this example, for simplicity, we allow for movement between the two statuses, but no births, deaths, or other forms of entry or exit to the system as a whole. The demographic accounting identities can be applied separately to each group,
\begin{align*}
    11 - 15 & = -5 + 1 \quad \text{(A)}\\
    14 - 10 & = -1 + 5 \quad \text{(B)}.
\end{align*}
When the accounting identities for each group are satisfied, the accounting identity for the system is a whole is necessarily satisfied as well.

@@

Publishers of age-structured demographic data typically use some variant of the following scheme,
\begin{center}
\includegraphics[width=0.4\textwidth]{figures_accounts/fig_account_withage2.pdf}
\end{center}
Population stocks stocks and flows are all disaggregated by the same age groups, which, in the case above, are ages 0, 1, and 2+. (The account in question might apply to non-human animals, or use a unit of measurement that is longer than a year.) The final age group includes everone over a certain age. Births are disaggregated by the age of the mother, rather than the age of the child being born, which is always 0.

@@

\begin{align}
    8 - (3 + 4) & = -2 + 3 - 1 & \text{Age 0 at $t+1$} \\   
    9 - 7 & = -(1 + 1) + (4 + 2) - (0 + 2) & \text{(Age 1 at $t+1$)} \\
    6 - (5 + 4) & = -(0 + 3 + 4) + (5 + 2 + 3) - (3 + 1 + 2) +  & \text{(Age 2+ at $t+1$)} \\
\end{align}
